---
title: "Dexmedetomidine MUE Analysis"
output:
  html_notebook: 
    code_folding: hide
    toc: yes
    toc_float: yes
---

```{r library, message=FALSE}
source("0-library.R")
tmp <- get_rds(dir.save)
library(tableone)
```

**Notes**

1. Groups: tmc = MH-TMC; mhhs = Rest of System
1. Data were calculated using Chi-Squared for categorical data and t-test or Mann-Whitney (noted by "nonnorm" in the *test* column) for continuous data.

## Patients

### Demographics
```{r demographics, results='asis'}
d <- data.demographics %>%
    mutate(sex = factor(sex, levels = c("Female", "Male")),
           race = factor(race, exclude = c("", "Unknown")),
           disposition = str_replace_all(disposition, regex(".*expired.*|.*hospice.*|.*deceased.*", ignore_case = TRUE), "Deceased/Hospice"),
           disposition = str_replace_all(disposition, regex(".*home.*|.*against.*", ignore_case = TRUE), "Home"),
           disposition = str_replace_all(disposition, regex(".*dc.*|.*transfer.*|.*care.*|.*skill.*", ignore_case = TRUE), "Transferred"))

vars <- c("age", "sex", "race", "length.stay", "disposition", "facility")
fvars <- c("sex", "race", "disposition", "facility")

tbl <- CreateTableOne(vars = vars, strata = "group", data = d, factorVars = fvars)
ptbl <- print(tbl, printToggle = FALSE, nonnormal = c("age", "length.stay"))

knitr::kable(ptbl, caption = "Demographics")
```

### SOFA Score

```{r sofa, results='asis'}
d <- data.sofa.score %>%
    inner_join(data.demographics[, c("pie.id", "group")], by = "pie.id") 

vars <- names(d)[-c(1, 9)]

tbl <- CreateTableOne(vars = vars, strata = "group", data = d)
ptbl <- print(tbl, printToggle = FALSE, nonnormal = vars)

knitr::kable(ptbl, caption = "SOFA")
```

**Notes**

1. The median score for each organ system, along with median total SOFA scores, are provided for each group.

#### Count of Patients with Each SOFA Score
```{r sofa2, results='asis'}
d <- data.sofa.score %>%
    inner_join(data.demographics[, c("pie.id", "group")], by = "pie.id") %>%
    group_by(group, sofa) %>%
    summarize(n = n()) %>%
    spread(sofa, n, fill = 0) %>%
    group_by(group)

knitr::kable(d, caption = "Count of SOFA Scores")
```

**Notes**

1. This data represents the number of patients with each SOFA score. This could be used to report the SOFA score in bins (ex: 0-6, 7-9, etc.).

### Substance Abuse

```{r substance, results='asis'}
d <- data.subabuse %>%
    inner_join(data.demographics[, c("pie.id", "group")], by = "pie.id") 

vars <- c("etoh.abuse", "etoh.high", "sub.abuse", "uds.pos")
fvars <- vars

tbl <- CreateTableOne(vars = vars, strata = "group", data = d, factorVars = fvars)
tbl <- print(tbl, printToggle = FALSE)

knitr::kable(tbl, caption = "Substance Abuse")
```

**Notes**

1. etoh.abuse and sub.abuse are based on ICD-9-CM codes for EtOH/substance abuse.
1. etoh.high = EtOH level was > 0.08
1. uds.pos = UDS was positive, excluding benzodiazepines and opiates

## Dexmedetomidine Therapy

### Indications
```{r indications, results='asis'}
d <- data.manual %>%
    inner_join(data.demographics[, c("pie.id", "group")], by = "pie.id") %>%
    mutate(icu.reason = str_trim(icu.reason, side = "both"),
           icu.reason = str_replace_all(icu.reason, "srug", "surg")) 

vars <- c("icu.reason", "dexmed.indication")
fvars <- vars

tbl <- CreateTableOne(vars = vars, strata = "group", data = d, factorVars = fvars)
tbl <- print(tbl, printToggle = FALSE, cramVars = "icu.reason")

knitr::kable(tbl, caption = "Indications")
```

### Dexmedetomidine Infusion

```{r dexmed, results='asis'}
d <- data.meds.cont.sum %>%
    filter(med == "dexmedetomidine") %>%
    inner_join(data.demographics[, c("pie.id", "group")], by = "pie.id") 

vars <- names(d[, -c(1, 2, 9)])
fvars <- "num.infusions"

tbl <- CreateTableOne(vars = vars, strata = "group", data = d, factorVars = fvars)
ptbl <- print(tbl, printToggle = FALSE, nonnormal = vars[-1])

knitr::kable(ptbl, caption = "Dexmedetomidine Infusion")
```

**Notes**

1. num.infusions = number of independent dexmedetomidine infusions; a new infusion was defined as > 12 hours off dexmedetomidine
1. cum.dose = cumulative dexmedetomidine dose received from all infusions, in micrograms / kg
1. cum.duration = total amount of time, in hours, from start to finish for all infusions; this includes time where the drip may have been off for a short period of time
1. cum.run.time = total amount of time, in hours, where the dexmedetomidine infusion was actually running
1. time.wt.avg = dexmedetomidine infusion rate across all infusions, in microgram/kg/hour
1. max.rate = maximum dexmedetomidine infusion rate, in microgram/kg/hour

### Concurrent Use of Continuous Sedatives / Analgesics

```{r sedativse, results='asis'}
d <- data.sedatives %>%
    inner_join(data.demographics[, c("pie.id", "group")], by = "pie.id") 

vars <- names(d[, -c(1, 9)])
fvars <- vars

tbl <- CreateTableOne(vars = vars, strata = "group", data = d, factorVars = fvars)
tbl <- print(tbl, printToggle = FALSE)

knitr::kable(tbl, caption = "Concurrent Sedatives")
```

**Notes**

1. There were no patients who received continuous morphine

## Mechanical Ventilation

```{r vent, results='asis'}
d <- data.vent %>%
    inner_join(data.demographics[, c("pie.id", "group")], by = "pie.id") %>%
    mutate(vent.times = as.character(vent.num),
           vent.times = ifelse(vent.num >= 3, ">/= 3", vent.times),
           vent.times = ordered(vent.times, levels = c("1", "2", ">/= 3")))

vars <- c("vent", "vent.times", "vent.duration", "dexm.vent.duration")
fvars <- c("vent", "vent.times")

tbl <- CreateTableOne(vars = vars, strata = "group", data = d, factorVars = fvars)
tbl <- print(tbl, printToggle = FALSE, nonnormal = c("vent.duration", "dexm.vent.duration"))

knitr::kable(tbl, caption = "Mechanical Ventilation")
```

**Notes**

1. vent.times = number of times patient was intubated
1. vent.duration = total time on ventilator, in hours, from all intubations
1. dexm.vent.duration = total time on ventilator and on dexmedetomidine, in hours

### RASS

```{r rass, results='asis'}
d <- data.rass %>%
    inner_join(data.demographics[, c("pie.id", "group")], by = "pie.id") 

vars <- names(data.rass)[-1]

tbl <- CreateTableOne(vars = vars, strata = "group", data = d)
ptbl <- print(tbl, printToggle = FALSE)

knitr::kable(ptbl, caption = "RASS")
```

**Notes**

1. Data represents the percent of time the RASS score was at goal (RASS of -1 or -2), above goal (RASS -3 to -5), or below goal (RASS of 0 to 4) in the 24-hours prior to dexmedetomidine initiation (pre), during dexmedetomidine, or in the 24-hours after dexmedetomidine (post)

## Safety Outcomes

```{r safety, results='asis'}
d <- data.safety %>%
    inner_join(data.demographics[, c("pie.id", "group")], by = "pie.id") 

vars <- c("hypotension", "bradycardia", "bp.change", "hr.change")
fvars <- c("hypotension", "bradycardia")

tbl <- CreateTableOne(vars = vars, strata = "group", data = d, factorVars = fvars)
tbl <- print(tbl, printToggle = FALSE, nonnormal = c("bp.change", "hr.change"))

knitr::kable(tbl, caption = "Safety")
```

**Notes**

1. Hypotension defined as *new* onset of SBP < 80 mmHg, MAP < 60, or requiring vasopressor initiation
1. Bradycardia defined as *new* onset of HR < 55 bpm or administration of atropine

## Cost

#### Dexmedetomidine Cost per Patient

```{r cost, results='asis'}
d <- data.cost.sum %>%
    inner_join(data.demographics[, c("pie.id", "group")], by = "pie.id") 

vars <- "cost"

tbl <- CreateTableOne(vars = vars, strata = "group", data = d)
ptbl <- print(tbl, printToggle = FALSE, nonnormal = vars)

knitr::kable(ptbl, caption = "Cost")
```

#### Dexmedetomidine Utilization by Product

```{r quantity, results='asis'}
knitr::kable(data.cost.prod, caption = "Product Utilization")
```

#### Dexmedetomidine Product Cost

```{r vials, results='asis'}
knitr::kable(data.dexmed.cost, caption = "Product Cost")
```

**Notes**

1. Average cost for FY 2015
2. Community hospitals did not use the 4 mcg/mL 100 mL bag

## References

#### SOFA Score
1. Vincent JL, et al. Intensive Care Med. 1996;22:707-10
1. Jones AE, et al. Crit Care Med. 2009;37:1649-54

#### Statistical Analysis

1. `r R.version.string` on a `r .Platform$OS.type` `r .Platform$r_arch` system
```{r citation, results='asis', echo=FALSE}
citation()
```

